Growth Dynamics of the Independent Gametophytes of *Pleurosoriopsis makinoi* (Polypodiaceae)

### 2019-05-07 ms.Rmd
Fix season as factor
was getting converted back to character

#' Format data for plotting: need columns to be mean and sd, by site and season.
paired_means <-
  paired_microclimate %>%
  select(-date) %>%
  group_by(site, season) %>%
  summarize_all(
    list(~mean(., na.rm = TRUE),
         ~sd(., na.rm = TRUE))
  ) %>%
  mutate(
    season = factor(season, levels = c("winter", "spring", "summer", "fall"))
  )

@@

  ) %>%
  arrange(season, var)

@@

#' Combine and write out.
subplots[[1]] +  subplots[[2]] +  subplots[[3]] +
  subplots[[4]] +  subplots[[5]] +  subplots[[6]] +
  subplots[[7]] +  subplots[[8]] +  subplots[[9]] +
  subplots[[10]] + subplots[[11]] + subplots[[12]] +
  plot_spacer() + legend + plot_spacer() + plot_layout(ncol = 3, heights = c(1, 1, 1, 1, 0.2))
```

```{r fig-6, fig.width=7, fig.height=8, fig.cap="Fig. 6. Relationships between growth of Pleurosoriopsis makinoi gametophytes (total cover, mean gemma number, and mean gemma length) and microclimate at the Okutama site. Microclimatic variables are monthly means of daily minimum relative humidity (%), daily mean temperature (°C), and daily light integral (DLI) (mol m-2 day-1). Grey bars show SD (except for total cover, which is a sum, not a mean). Significant relationships (linear model) shown with a line."}
#' Loop through all combination of dep and indep variables and their models,
#' and make plots for each.
var_grid <- make_var_grid (c("rh_min", "par_total", "temp_mean"))

>>>>

#' Format data for plotting: need columns to be mean and sd, by site and season.
paired_means <-
  paired_microclimate %>%
  select(-date) %>%
  group_by(site, season) %>%
  summarize_all(
    list(~mean(., na.rm = TRUE),
         ~sd(., na.rm = TRUE))
  )

@@

  ) %>%
  mutate(
    season = factor(season, levels = c("winter", "spring", "summer", "fall"))
  ) %>%
  arrange(season, var)

@@

#' Combine and write out.
subplots[[1]] +  subplots[[2]] +  subplots[[3]] + # Winter
subplots[[4]] +  subplots[[5]] +  subplots[[6]] + # Spring
subplots[[7]] +  subplots[[8]] +  subplots[[9]] + # Summer
subplots[[10]] + subplots[[11]] + subplots[[12]] + # Fall
plot_spacer() + legend + plot_spacer() + plot_layout(ncol = 3, heights = c(1, 1, 1, 1, 0.2))

ggsave(glue::glue("fig-5_{Sys.Date()}.pdf"), width = 7, height = 8, units = "in")
```

```{r fig-6, fig.width=7, fig.height=8, fig.cap="Fig. 6. Relationships between growth of *Pleurosoriopsis makinoi* gametophytes (total cover, mean gemma number, and mean gemma length) and microclimate at the Okutama site. Microclimatic variables are monthly means of daily light integral (DLI) (mol m^-2^ day^-1^), daily minimum relative humidity (%), and daily mean temperature (°C). Grey bars show SD (except for total cover, which is a sum, not a mean). Significant relationships (linear model) shown with a line."}
#' Loop through all combination of dep and indep variables and their models,
#' and make plots for each.
var_grid <- make_var_grid (c("rh_min", "par_total", "temp_mean"))
